### 2017-04-02 paper/evaluation.tex
fix subsections to dimensions
updated plots
starting rq5

    \begin{subfigure}{0.47\textwidth}
      \centering
      \includegraphics[width=\textwidth]{plots/testcost-long.pdf}
      \caption{\label{fig:longtcost}Long group}
    \end{subfigure}\\
    \vspace{2.5ex}
    \begin{subfigure}{0.47\textwidth}
      \centering
      \includegraphics[width=\textwidth]{plots/testcost-medium.pdf}
      \caption{\label{fig:medtcost}Medium group}
    \end{subfigure}\\
    \vspace{2.5ex}
    \begin{subfigure}{0.5\textwidth}
      \centering
      \begin{tabular}{rrrr}
        \toprule
        & $\sigma\leq1$ & $1<\sigma\leq5$ & $\sigma\ge5$ \\
        \midrule    
        Long   &  9 & 14 & 5 \\
        Medium & 17 & 20 & 7 \\
        \bottomrule
      \end{tabular}
      \caption{\label{fig:sd}\Fix{adjust values}}    
    \end{subfigure}%

@@

\subsection{Answering research question \numRQD{}}
\label{sec:rqD}

\begin{itemize}
    \item \emph{\RQD}
\end{itemize}

@@

\subsection{Answering research question \numRQC{}}
\label{sec:rqC}

@@

>>>>

    \begin{subfigure}{0.47\textwidth}
      \centering
      \includegraphics[width=\textwidth]{plots/testcost-long.pdf}
      \caption{\label{fig:longtcost}Long group}
    \end{subfigure}\\
    \vspace{2.5ex}
    \begin{subfigure}{0.47\textwidth}
      \centering
      \includegraphics[width=\textwidth]{plots/testcost-medium.pdf}
      \caption{\label{fig:medtcost}Medium group}
    \end{subfigure}\\
    \vspace{2.5ex}
    \begin{subfigure}{0.47\textwidth}
      \centering
      \includegraphics[width=\textwidth]{plots/boxplots-testcases.pdf}
      \caption{\label{fig:medtcost}Distribution of test cases per group}
    \end{subfigure}\\
    \vspace{2.5ex}
    \begin{subfigure}{0.5\textwidth}
      \centering
      \begin{tabular}{rrrr}
        \toprule
        & $\sigma\leq1$ & $1<\sigma\leq5$ & $\sigma\ge5$ \\
        \midrule    
        Long   &  9 & 14 & 5 \\
        Medium & 17 & 20 & 7 \\
        \bottomrule
      \end{tabular}
      \caption{\label{fig:sd}\Fix{adjust values}}    
    \end{subfigure}%

@@

\subsection{Effectiveness}
\label{sec:rqD}

\begin{itemize}
    \item \textbf{\RQD}
\end{itemize}

@@

\subsection{Adoption}
\label{sec:rqC}
\label{sec:rqE}

@@

\begin{itemize}
	\item \textbf{\RQE{}}
\end{itemize}

\Luis{rework this $\rightarrow$}
We considered the \numNonParallel{} subjects that do not use any
parallel mode from Section~\ref{sec:rqC} and elaborated a
quick survey to extent the comprehension about why developers do not
use parallel configuration. \Luis{describe how we created the survey}.
In total, we sent \emailsSent{} e-mails to developers that recently
contributed to the project and received \emailsAnswered{} answers.

\begin{center}
\fbox{
  \begin{minipage}{8cm}
      \textit{Answering \numRQE{}:~\emph{\Luis{summarize
	  findings...}}}
  \end{minipage}
}
\end{center}
